---
title: "IMDB"
output:
  pdf_document: default
  html_document: default
date: "2023-12-02"
---

```{r}
myData <- read.csv("movie_metadata_original.csv")
movie_data <- read.csv("movie_metadata_original.csv")
head(myData)
```
```{r}
sum(is.na(myData))
```
```{r}
nrow(myData)
```
```{r}
library(ggplot2)
```

#Summary Statistics
```{r}
summary(movie_data)
```

#Data Structure
```{r}
str(movie_data)
```

#Visualization

#Histograms

#Histogram num_critic_for_reviews
#Saving Histogram to a PNG file
```{r}
png("num_critic_for_reviews",width = 800,height = 600)
```
#Create Histogram
```{r}
hist(movie_data$num_critic_for_reviews)
```

#Histogram duration 
#Saving Histogram to a PNG file
```{r}
png("duration ",width = 800,height = 600)
```
#Create Histogram
```{r}
hist(movie_data$duration)
```

#Histogram director_facebook_likes 
#Saving Histogram to a PNG file
```{r}
png("director_facebook_likes ",width = 800,height = 600)
```
#Create Histogram
```{r}
hist(movie_data$director_facebook_likes)
```
#create histogram using ggplot2
```{r}
histogram<-ggplot(movie_data,aes(x=duration))+
  geom_histogram(binwidth = 10,fill="white",color="black")+
  labs(x="Duration in Minutes", y="Frequency",title="Histogram of Movie Duration")
```
#Save the histogram as a PNG file
```{r}
ggsave("durtion_histogram_ggplot.png",plot=histogram, width=8,height = 6, units = "in")
```


#Histogram num_voted_users 
#Saving Histogram to a PNG file
```{r}
png("num_voted_users ",width = 800,height = 600)
```
#Create Histogram
```{r}
hist(movie_data$num_voted_users)
```

#Histogram cast_total_facebook_likes
#Saving Histogram to a PNG file
```{r}
png("cast_total_facebook_likes ",width = 800,height = 600)
```
#Create Histogram
```{r}
hist(movie_data$cast_total_facebook_likes)
```

#Histogram facenumber_in_poster 
#Saving Histogram to a PNG file
```{r}
png("facenumber_in_poster ",width = 800,height = 600)
```
#Create Histogram
```{r}
hist(movie_data$facenumber_in_poster)
```

#Histogram num_user_for_reviews 
#Saving Histogram to a PNG file
```{r}
png("num_user_for_reviews ",width = 800,height = 600)
```
#Create Histogram
```{r}
hist(movie_data$num_user_for_reviews)
```

#Histogram actor_2_facebook_likes 
#Saving Histogram to a PNG file
```{r}
png("actor_2_facebook_likes ",width = 800,height = 600)
```
#Create Histogram
```{r}
hist(movie_data$actor_2_facebook_likes)
```

#Histogram imdb_score 
#Saving Histogram to a PNG file
```{r}
png("imdb_score ",width = 800,height = 600)
```
#Create Histogram
```{r}
hist(movie_data$imdb_score)
```

#Histogram movie_facebook_likes 
#Saving Histogram to a PNG file
```{r}
png("movie_facebook_likes ",width = 800,height = 600)
```
#Create Histogram
```{r}
hist(movie_data$movie_facebook_likes)
```

```{r}
numeric_cols <- sapply(myData, is.numeric)

detect_outliers <- function(x, na.rm = TRUE) {
  qnt <- quantile(x, probs=c(0.25,0.75), na.rm = na.rm)
  H <- 1.5 * IQR(x, na.rm = na.rm)
  return(x < (qnt[1] - H) | x > (qnt[2] + H))
}

outliers_logical <- apply(myData[, numeric_cols], 2, detect_outliers)

rows_with_outliers <- apply(outliers_logical, 1, any)

myData_filtered <- myData[!rows_with_outliers, ]

```


```{r}
nrow(myData_filtered)

```
```{r}
set.seed(2)
sampled_data <- myData_filtered[sample(nrow(myData), 2101), ]

```

```{r}
  sampled_data <- na.omit(sampled_data)

```

```{r}
str(sampled_data)

```

```{r}

# Install
#install.packages("tm")
#install.packages("wordcloud")
#install.packages("SnowballC") # for text stemming
#install.packages("RColorBrewer") # color palettes
library(tm)
library(wordcloud)
library("SnowballC")
library("RColorBrewer")
```

# Regression preparation

```{r}
filtered_sampled_data <- subset(sampled_data, language == "English")
filtered_sampled_data <- subset(filtered_sampled_data, country == "USA")
View(filtered_sampled_data)

```

```{r}
column_names <- colnames(filtered_sampled_data)
print(column_names)

```

```{r}
sampled_data_regression <- filtered_sampled_data[, !(colnames(filtered_sampled_data) %in% c('director_name', 'movie_title', 'actor_2_name', 'genres', 'actor_1_name', 'plot_keywords', 'language', 'country', 'actor_1_facebook_likes', 'actor_2_facebook_likes'))]

```

# Linear Regression

```{r}
Model1 <- lm(imdb_score ~ . , data =  sampled_data_regression)
summary(Model1)

```
```{r}
Model2 <- lm(imdb_score ~ num_critic_for_reviews + num_voted_users + cast_total_facebook_likes + facenumber_in_poster + budget + title_year + actors_facebook_likes + profits  + movie_facebook_likes , data =  sampled_data_regression)
summary(Model2)

```
```{r}
Model5 <- lm(imdb_score ~ num_voted_users + cast_total_facebook_likes + facenumber_in_poster + title_year + actors_facebook_likes + profits  + movie_facebook_likes , data =  sampled_data_regression)
summary(Model5)

```


```{r}
Model3 <- lm(gross ~ . , data =  sampled_data_regression)
summary(Model3)

```

```{r}
Model4 <- lm(gross ~ num_critic_for_reviews + num_voted_users + cast_total_facebook_likes + facenumber_in_poster + budget + title_year + actors_facebook_likes + profits  + movie_facebook_likes  , data =  sampled_data_regression)
summary(Model4)

```

```{r}
Model6 <- lm(gross ~ num_critic_for_reviews + num_voted_users + cast_total_facebook_likes + facenumber_in_poster + title_year + actors_facebook_likes + movie_facebook_likes  , data =  sampled_data_regression)
summary(Model6)

```

```{r}
#install.packages("lmtest")
library(lmtest)

lr_test <- lrtest(Model1, Model2, Model3, Model4, Model5, Model6)
print(lr_test)

```

```{r}
nrow(sampled_data_regression)
TData <- sampled_data_regression[1:515,]
VData <- sampled_data_regression[516:858,]

Model11 <- lm(imdb_score ~ . , data =  TData)
Model22 <- lm(imdb_score ~ num_critic_for_reviews + num_voted_users + cast_total_facebook_likes + facenumber_in_poster + budget + title_year + actors_facebook_likes + profits  + movie_facebook_likes , data =  TData)
Model55 <- lm(imdb_score ~ num_voted_users + cast_total_facebook_likes + facenumber_in_poster + title_year + actors_facebook_likes + profits  + movie_facebook_likes , data =  TData)

Model33 <- lm(gross ~ . , data =  TData)
Model44 <- lm(gross ~ num_critic_for_reviews + num_voted_users + cast_total_facebook_likes + facenumber_in_poster + budget + title_year + actors_facebook_likes + profits  + movie_facebook_likes  , data =  TData)
Model66 <- lm(gross ~ num_critic_for_reviews + num_voted_users + cast_total_facebook_likes + facenumber_in_poster + title_year + actors_facebook_likes + movie_facebook_likes  , data =  TData)

Pred1 <- predict(Model11, VData)
Pred2 <- predict(Model22, VData)
Pred5 <- predict(Model55, VData)

print(sqrt(mean(VData$imdb_score-Pred1)^2))
print(sqrt(mean(VData$imdb_score-Pred2)^2))
print(sqrt(mean(VData$imdb_score-Pred5)^2))

Pred3 <- predict(Model11, VData)
Pred4 <- predict(Model22, VData)
Pred6 <- predict(Model55, VData)

print(sqrt(mean(VData$imdb_score-Pred3)^2))
print(sqrt(mean(VData$imdb_score-Pred4)^2))
print(sqrt(mean(VData$imdb_score-Pred6)^2))

```

# Linear Regression

```{r}
Model <- lm(imdb_score ~ . , data =  sampled_data_regression)
summary(Model)

```

```{r}
Model <- lm(gross ~ . , data =  sampled_data_regression)
summary(Model)

```
```{r}
library(ggplot2)
```

#Creating Scatter Plot between imdb score and variables highly correlated with IMDB score

#scatter plot between duration and imdb score
```{r}
plot(sampled_data_regression$duration,sampled_data_regression$imdb_score,
     xlab = "duration", ylab = "imdb_score",
     main = "Scatter Plot: Duration vs. IMDB score")
```
#scatter plot between num_voted_users and imdb score
```{r}
plot(sampled_data_regression$num_voted_users,sampled_data_regression$imdb_score,
     xlab = "num_voted_users", ylab = "imdb_score",
     main = "Scatter Plot: num_voted_users vs. IMDB score")
```
```{r}
library(scales)
```

#Financial & Social Metrics
#scatter plot between budget and gross
```{r}
ggplot(sampled_data_regression, aes(x = budget / 1e6, y = gross / 1e6)) +
  geom_point() +
  labs(x = "Budget (in millions)", y = "Gross Earnings (in millions)", 
       title = "Scatter Plot: Budget vs Gross Earnings") +
  scale_x_continuous(labels = scales::label_number_si()) +
  scale_y_continuous(labels = scales::label_number_si())
```
# Scatter plot between 'movie_facebook_likes' and 'imdb_score' with labels in millions
```{r}
ggplot(sampled_data_regression, aes(x = movie_facebook_likes / 1e6, y = imdb_score)) +
  geom_point() +
  labs(x = "Movie Facebook Likes (in millions)", y = "IMDb Score", 
       title = "Scatter Plot: Movie Facebook Likes vs IMDb Score") +
  scale_x_continuous(labels = scales::label_number_si())

```

Scatter plot between 'director_facebook_likes' and 'imdb_score'


# Scatter plot between 'cast_total_facebook_likes' and 'imdb_score'
```{r}
ggplot(sampled_data_regression, aes(x = cast_total_facebook_likes, y = imdb_score)) +
  geom_point() +
  labs(x = "Cast Total Facebook Likes", y = "IMDb Score",
       title = "Scatter Plot: Cast Total Facebook Likes vs IMDb Score")

```

#Review & Reception Metrics
# Scatter plot between 'num_critic_for_reviews' and 'imdb_score'
```{r}
ggplot(sampled_data_regression, aes(x = num_critic_for_reviews, y = imdb_score)) +
  geom_point() +
  labs(x = "Number of Critic Reviews", y = "IMDb Score",
       title = "Scatter Plot: Num Critic Reviews vs IMDb Score")

```

# Scatter plot between 'num_user_for_reviews' and 'imdb_score'
```{r}
ggplot(sampled_data_regression, aes(x = num_user_for_reviews, y = imdb_score)) +
  geom_point() +
  labs(x = "Number of User Reviews", y = "IMDb Score",
       title = "Scatter Plot: Num User Reviews vs IMDb Score")

```

#R Code for Correlation Analysis
# Calculate correlation between 'gross' and 'imdb_score'
```{r}
correlation_result <- cor(sampled_data_regression$gross, sampled_data_regression$imdb_score)
```
# Print the correlation coefficient
```{r}
print(correlation_result)
```
# Interpretation based on the correlation coefficient

```{r}
if (correlation_result > 0) {
  cat("There is a positive correlation between gross earnings and IMDb ratings.\n")
} else if (correlation_result < 0) {
  cat("There is a negative correlation between gross earnings and IMDb ratings.\n")
} else {
  cat("There is no linear relationship between gross earnings and IMDb ratings.\n")
}
```

```{r}

sample_index <- sample(nrow(sampled_data_regression), size=nrow(sampled_data_regression)*0.90, replace=F)

train_valid <- sampled_data_regression[sample_index,]
test <- sampled_data_regression[-sample_index,]

library(caret)

myCtrl <- trainControl(method="cv",
                       number=10)
myGrid <- expand.grid(.k=c(1:15))
set.seed(1)
knn_imdb <- train(as.numeric(imdb_score)~., 
                    data=train_valid,
                    method="knn",
                    trControl=myCtrl,
                    tuneGrid=myGrid,
                    preProc=c("center","scale"))

knn_imdb

```

```{r}

predicted_imdb <- predict(knn_imdb,
                            newdata=test,
                            type='raw') 

forecast::accuracy(predicted_imdb,test$imdb_score)
```
